\section{Relevant Projects}
\begin{itemize}
 \item \textbf{Pai-deia} | \href{http://alseambusher.github.io/Paideia}{alseambusher.github.io/Paideia} | \textbf{Java, C++, Android, Deep Learning}\\
 This is a Deep Learning based android app that uses Tensorflow and detects objects around you though camera and maps it into one of the classes in Imagenet and then pulls more information about what the user is seeing from Wikipedia and Wolfram Alpha. The results are also tweaked based on a learning model that monitors user's activity and shows more relevant content over time.

 \item \textbf{Santander Customer Satisfaction} | \textbf{Python, XGBoost, Kaagle}\\
In this project, I worked on a Kaggle problem by Santander to classify which customers are happy. It was a binary classification problem with 371 unknown attributes, 76,020 samples for training and 75,818 samples for testing. We used techniques such as outlier detection with clustering, dimensionality reduction, feature engineering, cross validation and classification to arrive at the final result with an accuracy of 84.27\%.

 %\item \textbf{Jarvis} | \href{http://github.com/alseambusher/jarvis}{github.com/alseambusher/jarvis} | \textbf{Python, opencv, gtk}\\
 %This is a Human Computer Interaction tool in python using which it is possible to control your Linux system using hand gestures. Users can add their own gestures and assign custom actions using a gtk ui. In order to accommodate any gesture defined by the user, I developed a state transition based approach to do so and published a paper at ICACCI- 2013.
 %\href{https://github.com/alseambusher/jarvis}{https://github.com/alseambusher/jarvis}
 %\item \textbf{QuickFoods} \\ This is an innovative app for hotels to manage their orders with ease even in rush hours. It mainly aims at reducting the time taken to complete the order cycle by bridging the gap between waiters and kitchen. This was built in Intuit LABS and received a lot traction from several five star hotels.

 % \item \textbf{Crontab-ui} | \href{http://npmjs.com/package/crontab-ui}{npmjs.com/package/crontab-ui} | \textbf{JavaScript, node.js}\\
 % This is a node.js tool available through npm that can be used to manage cron jobs across systems very easily. With features such as import, export, backup, error logging of jobs, this is an end-to-end tool to manage crontab efficiently. This is being used by thousands of people including several companies.

 %\item \textbf{Columbus} | \href{http://github.com/alseambusher/columbus}{github.com/alseambusher/columbus} | \textbf{Python, Machine Learning}\\
 %A python based service discovery tool using which we can combine web services automatically to perform composite tasks. Using techniques such as web crawling, feature extraction, k-means clustering, a Service dependency graph (SDG) is generated. Composite services are discovered by a search algorithm in this SDG.

 \item \textbf{Social Event Detection} | \href{http://github.com/alseambusher/SED}{github.com/alseambusher/SED} | \textbf{Python, Machine Learning}\\
In this project, I discovered event-related multimedia and organized them in event-specific clusters, within a collection of Web multimedia. The dataset was multimodal – images along with
metadata such as location, description and timestamps. SIFT features were extracted from images to represent them numerically. Then we used an easy to obtain supervisory signal and a SVM classifier to perform multimodal clustering to detect social events.

 %\item \textbf{A Real Time Multiplayer Gaming Network Platform as a Service} - As multiplayer games are becoming more and more complex, there is a need of a simpler way for game developers to manage network. I built a network framework in C++ and Python using which issues such as latency, load balancing, bad connectivity etc. can be addressed through a service.\\
 %\textit{Code: github.com/alseambusher/Easy-Multi-Player}
 %\href{https://github.com/alseambusher/Easy-Multi-Player}{https://github.com/alseambusher/Easy-Multi-Player}
\end{itemize}
\vspace{5pt}
